Reproduction and Expansion of \\"SPECIALIZATION TRENDS IN ECONOMICS RESEARCH" by Sebastian Galiani, Ramiro H. Gálvez, and Ian Nachman

### 2025-02-13 documents/paper.tex
Document missing urls and discussion papers.

>>>>

There are 6 digits in the current range without a corresponding discussion paper accessible.
The numbers are (4953, 12119, 12315, 12577, 12664, 16580).
The first discussion paper would have been from May 2010.
The later five ones fall into the time span January 2019 to November 2023.

There are 9 discussion paper entries without a corresponding discussion paper file accessible.
The numbers are (9, 18, 21, 28, 33, 56, 173, 16801, 17143).
The first nine fall into the range June 1998 to July 2000.
The later two are from February and July 2024.
